Tensor anisotropy as a tracer of cosmic voids

### 2015-02-21 cosmic_voids.tex
Little typo. Correcting figure 3, legend of over and subcompensated voids.
Correcting over-subcompensated values. Little typos

\begin{abstract}
We present a new method to find voids in cosmological simulations
based on algorithms that use the tidal and the velocity shear tensors
to locally define the cosmic web. 
We use show that fractional anisotropy (FA) computed from the eigenvalues
of each web scheme is a good void tracers. 
Based on this result we identify voids using a watershed
transform based on the local minima of the FA field.
This void identification technique does not make any assumption on the
shape or structure of the voids. 
We test the method on the Bolshoi simulation and report on the
abundance and radial averaged profiles for the density, velocity and
fractional anistropy.
We find that voids in the velocity shear web are smaller than voids in
the tidal web, with a particular overabundance of very small voids in
the inner region of filaments/sheets.
We clasify voids as overcompansated/subcompensated depending on the
presence/absence of an overdense matter ridge in their density
profile, finding that close to $65\%$ and $35\%$  of the total
population are classified into each category, respectively.
Finally, we find evidence for the existence of universal profiles once the
radial coordinate is normalized to the effective radius of each void
from the radiallly averaged profiles for density, velocity and
fractional anisotropy. 
\end{abstract}

@@

Cosmic voids are one of the most striking features of the
Universe on its larges scales since they were found in the first
galaxy surveys \citep{Chincarini75, Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87}.  
However, due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through modern galaxy surveys such as the two-degree field Galaxy
Redshift Survey (2dF) \citep{ Colless01, Colless03} and the Sloan
Digital Sky Survey (SDSS)\citep{York00, Abazajian03}.
These observational breakthughs generated a great interest in the last
decade to study voids \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

On the theoretical side the basic framework that explains
the origin of voids was established in the seminal work of
\citet{Zeldovich70} and refined in the following decades.  
The first detailed theoretical models describing formation, dynamics
and properties of  voids \citep{Hoffman82, Icke84, Bertschinger85,
  Blumenthal92} were  complemented and extended by numerical studies
\citep{Martel90, Regos91, Weygaert93, Dubinski93, Bond96}. 
Currently, the most popular approach to study voids relies on N-body
simulations. For an extensive compilation of previous  
numerical works we refer the reader to \citet{Colberg08}.

@@

The FA is defined as follows.
%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{{\mathrm{FA}} = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} },}
%.........................................................................
where the eigenvalues can be taken from either the T-Web or the V-Web 
(FA-T-Web and FA-V-Web respectively). Such as it is defined, FA$=0$ 
corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) 
and FA$=1$ to a highly anisotropic distribution.

@@

Table \ref{tab:number_voids} lists the number of voids in 
each effective radius bin For the two web finding methods.

@@

Figure \ref{fig:density_profile} shows the results of stacked density
profiles for different void sizes.  
We normalize the radial coordinate with the effective radius to check
for possible universal features among voids. 
We calculate the profile out to a radius $8\ \reff$  to capture the
the point where the overdensity reaches the mean value.

@@

A second feature about these profiles is their steepnes at inner
regions.  
In subcompensated voids, larger voids are steeper.
Smaller voids exhibit moderate slopes, reaching the mean density at
larger radii than larger voids.
This suggests that smaller subcompensated voids are embedded into low
density structures like voids or walls, while arge subcompensated
voids are surrounded  by dense structures, reaching the mean density
at lower effective radii than smaller voids.
In overcompensated voids larger voids reach first  both the
compensation ridge and then the mean density value.

@@

On the other hand, overcompensated voids initially exhibit and outward
profiles, (as expected from a low density region) and approximately at
the radius of the compensation ridge, the velocity reaches a peak,
decreases and becomes negative, showing the infalling flow of matter
further than the compensation ridge. 
This shows that the high density structures associated to the
compensation ridge dominate the matter flow both from inside and
outside the void.

@@

We recognize that our choice produces smaller voids as compared with
other voids finding methods, however this has the advantange of
voiding the contamination from external structures.

@@

A second step in the characterization of the voids found by our method
was the separation into subcompensated and overcompensated samples. 
In the T-Web $60\%$ of the voids are overcompensated, meaning that
they are located in denser regions with a clear delimiting ridge. 
For the V-web the overcompensated fraction increases from $60\%$ to
$80\%$ as the void size decreases, supporting the picture of smaller
spurious voids located in matter sheets.

@@

In other studies where voids are found using considerations on the
density fields the ridge is, almost by definition, located around
$r/r_{\rm eff}\sim 1$ and the subcompensated voids reach average
density around $r/r_{\rm eff}\sim 3$. 
This indicates that voids defined by FA boundaries are close smaller 
than voids found by density only considerations close by a factor of
$2$.

>>>>

\begin{abstract}
We present a new method to find voids in cosmological simulations
based on algorithms that use the tidal and the velocity shear tensors
to locally define the cosmic web. 
We show that fractional anisotropy (FA) computed from the eigenvalues
of each web scheme is a good void tracer. 
Based on this result we identify voids using a watershed
transform based on the local minima of the FA field.
This void identification technique does not make any assumption on the
shape or structure of the voids. 
We test the method on the Bolshoi simulation and report on the
abundance and radial averaged profiles for the density, velocity and
fractional anistropy.
We find that voids in the velocity shear web are smaller than voids in
the tidal web, with a particular overabundance of very small voids in
the inner region of filaments/sheets.
We clasify voids as subcompensated/overcompansated depending on the
absence/presence of an overdense matter ridge in their density
profile, finding that close to $65\%$ and $35\%$ of the total
population are classified into each category, respectively.
Finally, we find evidence for the existence of universal profiles once the
radial coordinate is normalized to the effective radius of each void
from the radiallly averaged profiles for density, velocity and
fractional anisotropy. 
\end{abstract}

@@

Cosmic voids are one of the most striking features of the
Universe on its larges scales since they were found in the first
galaxy surveys \citep{Chincarini75, Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87}.  
However, due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through modern galaxy surveys such as the two-degree field Galaxy
Redshift Survey (2dF) \citep{ Colless01, Colless03} and the Sloan
Digital Sky Survey (SDSS)\citep{York00, Abazajian03}.
These observational breakthroughs generated a great interest in the last
decade to study voids \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

On the theoretical side, the basic framework that explains
the origin of voids was established in the seminal work of
\citet{Zeldovich70} and refined in the following decades.  
The first detailed theoretical models describing formation, dynamics
and properties of  voids \citep{Hoffman82, Icke84, Bertschinger85,
  Blumenthal92} were  complemented and extended by numerical studies
\citep{Martel90, Regos91, Weygaert93, Dubinski93, Bond96}. 
Currently, the most popular approach to study voids relies on N-body
simulations. For an extensive compilation of previous  
numerical works we refer the reader to \citet{Colberg08}.

@@

The FA is defined as follows
%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{{\mathrm{FA}} = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} },}
%.........................................................................
where the eigenvalues can be taken from either the T-Web or the V-Web 
(FA-T-Web and FA-V-Web respectively). Such as it is defined, FA$=0$ 
corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) 
and FA$=1$ to a highly anisotropic distribution.

@@

Table \ref{tab:number_voids} lists the number of voids in 
each effective radius bin for the two web finding methods.

@@

Figure \ref{fig:density_profile} shows the results of stacked density
profiles for different void sizes.  
We normalize the radial coordinate with the effective radius to check
for possible universal features among voids. 
We calculate the profile out to a radius $8\ \reff$  to capture the
point where the overdensity reaches the mean value.

@@

A second feature about these profiles is their steepnes at inner
regions.  
In subcompensated voids, larger voids are steeper.
Smaller voids exhibit moderate slopes, reaching the mean density at
larger radii than larger voids.
This suggests that smaller subcompensated voids are embedded into low
density structures like voids or walls, while large subcompensated
voids are surrounded  by dense structures, reaching the mean density
at lower effective radii than smaller voids.
In overcompensated voids larger voids reach first  both the
compensation ridge and then the mean density value.

@@

On the other hand, overcompensated voids initially exhibit outward
profiles, (as expected from a low density region) and approximately at
the radius of the compensation ridge, the velocity reaches a peak,
decreases and becomes negative, showing the infalling flow of matter
further than the compensation ridge. 
This shows that the high density structures associated to the
compensation ridge dominate the matter flow both from inside and
outside the void.

@@

We recognize that our choice produces smaller voids as compared with
other voids finding methods, however this has the advantage of
avoiding the contamination from external structures.

@@

A second step in the characterization of the voids found by our method
was the separation into subcompensated and overcompensated samples. 
In the T-Web $35\%$ of the voids are overcompensated, meaning that
they are located in denser regions with a clear delimiting ridge. 
For the V-web the subcompensated fraction increases from $65\%$ to
$85\%$ as the void size decreases, supporting the picture of smaller
spurious voids located in low density matter sheets.

@@

In other studies where voids are found using considerations on the
density fields the ridge is, almost by definition, located around
$r/r_{\rm eff}\sim 1$ and the subcompensated voids reach average
density around $r/r_{\rm eff}\sim 3$. 
This indicates that voids defined by FA boundaries are smaller 
than voids found by density only considerations close by a radial factor 
of $2$.
